Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Reputation Mechanism in Information Security

\subsection{Reputation Mechanism in Information Security}
The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system, \cite{ref_41_reputation, ref_44_reputation}.
In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust. This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
In 2015, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor network and cloud computing to calculate and manage trust and reputation of the service of CSP and SNP \cite{ref_47_reputation}.
In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance rule that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}. The nodes get lower discourse rights and reputation in the voting process if any malicious behavior is detected by the system. Furthermore, they presented a reputation-based primary change scheme. The node with a higher reputation would get greater opportunities to generate new valid blocks, which reduces the security risk of the system.
In 2020, Chouikhi \textit{et al.} built a model for reputation computing and a credibility model to enhance network efficiency \cite{ref_23_reputation}. They used the reputation score or value to measure the behavior of a vehicle towards other vehicles and network services. And the credibility of vehicles is used to determine the accuracy of a reputation score offered by a vehicle. 
In the same year, Wen \textit{et al.} proposed a Dirichlet reputation-based scheme and adopt the reputation score to select a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}. Furthermore, they developed an artificial noise detection method with multiple thresholds. They provided ratings with multiple graded levels. In the Dirichlet reputation-based scheme, the graded ratings were directly expressed and reflected in the derived reputation scores.
In 2021, Liang \textit{et al.} presented a Markov-based reputation scheme in an intrusion detection system. The Hidden Generalized Mixture Transition Distribution (HgMTD) model, namely RS-HgMTD, is developed to assist each vehicle in the VANET to measure the creditworthiness of its neighbor vehicles \cite{ref_46_reputation}.

>>>>

\subsection{Reputation Mechanism in Information Security}
The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system, \cite{ref_41_reputation, ref_44_reputation}.
In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust. This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
To calculate and manage trust and reputation of CSP and SNP services, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor networks and cloud computing in 2015 \cite{ref_47_reputation}.
Lei \textit{et al.} presented a reputation-based Byzantine Fault Tolerance rule in 2018, which uses a reputation model to assess the performance of each node in the blockchain system \cite{ref_25_reputation}. If the system detects any malicious behavior, the nodes' discourse rights and reputation in the voting process are reduced. They also provided a primary change method based on reputation. The node with a higher reputation would have more chances to generate fresh valid blocks, lowering the system's security risk.
In 2020, Chouikhi \textit{et al.} developed a reputation computing and credibility model to improve network efficiency \cite{ref_23_reputation}. They measured a vehicle's behavior toward other vehicles and network services using its reputation score or worth. And a vehicle's credibility is utilized to determine the correctness of a reputation score it offers.
In the same year, Wen \textit{et al.} designed a Dirichlet reputation-based approach, and used the reputation score to choose a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}. Furthermore, they devised a multi-threshold fake noise detection approach. They gave ratings on a scale of one to ten. The graded ratings were directly represented and reflected in the generated reputation scores in the Dirichlet reputation-based method.
In 2021, Liang \textit{et al.} introduced an intrusion detection system with a Markov-based reputation algorithm \cite{ref_46_reputation}. The RS-HgMTD model of the Hidden Generalized Mixture Transition Distribution (HgMTD) is designed to help each vehicle in the VANET assess the creditworthiness of its neighbors.
